This is an example of article title

### 2025-10-30 paper/paper.tex
bump version.
Add a final short argument on the code.

\newcommand{\term}[1]{\emph{#1}}
\newcommand{\e}{\ensuremath{\mathrm{e}}}
\newcommand{\im}{\ensuremath{\mathrm{i}}}
\newcommand{\LieGroupsVersion}{0.1.6}
%
% Define muted colors.
\definecolor{TolMutedBlue}{HTML}{332288}
\definecolor{TolMutedCyan}{HTML}{88CCEE}
\definecolor{TolMutedTeal}{HTML}{44AA99}
\definecolor{TolMutedGreen}{HTML}{117733}
\definecolor{TolMutedOlive}{HTML}{999933}
\definecolor{TolMutedSand}{HTML}{DDCC77}
\definecolor{TolMutedRose}{HTML}{CC6677}
\definecolor{TolMutedWine}{HTML}{882255}
\definecolor{TolMutedPurple}{HTML}{AA4499}
%
\hypersetup{colorlinks=true}
%
\begin{document}

@@

@@

The resulting Bézier curves on both Lie groups are shown in Figure~\ref{fig:Bezier}.
One can see that the product Lie group works the same as if one would have done that
separately component-wise, while the Bézier curve on \(\mathrm{SE}(2)\) behaves differently.

>>>>

\newcommand{\term}[1]{\emph{#1}}
\newcommand{\e}{\ensuremath{\mathrm{e}}}
\newcommand{\im}{\ensuremath{\mathrm{i}}}
\newcommand{\LieGroupsVersion}{0.1.7}
%
% Define muted colors.
\definecolor{TolMutedBlue}{HTML}{332288}
\definecolor{TolMutedCyan}{HTML}{88CCEE}
\definecolor{TolMutedTeal}{HTML}{44AA99}
\definecolor{TolMutedGreen}{HTML}{117733}
\definecolor{TolMutedOlive}{HTML}{999933}
\definecolor{TolMutedSand}{HTML}{DDCC77}
\definecolor{TolMutedRose}{HTML}{CC6677}
\definecolor{TolMutedWine}{HTML}{882255}
\definecolor{TolMutedPurple}{HTML}{AA4499}
%
\hypersetup{colorlinks=true}
%
\begin{document}

@@

A central function on the Lie algebra is the Lie bracket $[\cdot, \cdot]\colon \frak g \times \frak g \to \frak g$, which is available as \verb|lie_bracket(|$\frak g$\verb|, X, Y)|.
% \footnote{in-place variant \texttt{lie\_bracket!($\frak g$, Z, X, Y)}.}
For more details on the Lie bracket see~\cite[Ch.~5]{HilgertNeeb:2012}.

@@

The resulting Bézier curves on both Lie groups are shown in Figure~\ref{fig:Bezier}.
One can see that the product Lie group works the same as if one would have done that
separately component-wise, while the Bézier curve on \(\mathrm{SE}(2)\) behaves differently.
A main feature here is, that due to the generic implementation on arbitrary Lie groups,
we can easily switch between different Lie groups, where the data is still valid.
